% Document class and font size
\documentclass[a4paper]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.4in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks
\hypersetup{
  pdftitle={Manoj Manikandan Resume},
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=blue,
  pdftitle={Resume - Manoj Manikandan},
}

% Formatting
\setlist{noitemsep, leftmargin=12pt, rightmargin=15pt, topsep=1.25pt}
% Removes item separation
\titleformat{\section}{\bfseries}{\large\thesection}{1pt}{}[\titlerule]
% Section title format
\titlespacing*{\section}{0.5pt}{*0.75}{*0.75} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
  \textbf{\Large MANOJ MANIKANDAN}\\[2pt] % Name
  \href{mailto:manojmani1408@gmail.com}{\underline{manojmani1408@gmail.com}}
  $|$ \href{tel:447543823791}{\underline{+44 7543823791}}  $|$
  \href{https://www.linkedin.com/in/manojmanikandan}{\underline{linkedin.com/in/manojmanikandan}}
  $|$
  \href{https://github.com/manojmanikandan7}{\underline{github.com/manojmanikandan7}}
\end{center}
% Education Section
\section*{EDUCATION}
\textbf{The University of Manchester} | Manchester, United Kingdom
\hfill Sep 2023 | Jun 2026\\ % University name and location
\textit{Bachelor of Science (Honours) Computer Science} \hfill
\textbf{Expected: First-Class Honours} % Degree and GPA
\begin{itemize}
  \item \textbf{Year 2: } \textbf{81\%}, \textbf{Top 15} in a class
    of \textbf{300}.
  \item \textbf{Courses:} Software Engineering, Data Structures and
    Algorithms, Artificial Intelligence, Machine Learning, \\
    Distributed Systems, Database Systems, Processor
    Micro-architecture, Operating Systems. %Computer Architecture,
    % Computer Engineering,
    % \item Student Representative and Ambassador for the Department
    % of Computer Science.
\end{itemize}

%\hfill Credit standing: Honors % Additional info
% \noindent
% \textbf{JSS INTERNATIONAL SCHOOL} | Dubai, United Arab Emirates
% \hfill Jun 2015 | Mar 2023\\ % University name and location
% \textit{High School Diploma - affiliated with CISCE} \hfill
% \textbf{Grade: 97\%} % Degree and GPA

% Experience Section
\section*{EXPERIENCE}
% \textbf{University of Manchester} \\ %\hfill City, State\\ %
% Company name and location
% \textit{Technology Intern} \hfill Apr 2023 | Aug 2023 % Position and duration
%\begin{itemize}
%\item Attained insight on Generative AI, utilising LLMs provided by
% OpenAI and Meta.  % Job responsibilities and achievements
%\item Designed a working chatbot to generate around 18 types of HR
% documents, planned to be incorporated in the system.
%\item Increased the efficiency of running basic operations around
% the workspace by 50\%.
%\item Acquired skills in code documentation, presentation, testing
% and technical writing.
%\item Mentored under a Machine Learning expert to complete my project.

%\end{itemize}
\textbf{N8 Computationally Intensive Reasearch} \hfill Jul 2025 | Aug 2025 \\
\textit{Research Software Engineer Intern}
\href{https://n8cir.org.uk/themes/internships/internships-2025/manchester/}{[Profile
Link]}\hfill Manchester, United Kingdom % Company name and
% location\\ % Position and duration
\begin{itemize}
  \item Collaborated with \textbf{7 academics} to drive digitization
    initiatives in humanities fields, spearheading \textbf{6 projects}.
  \item Remodeled the codebase of the
    \href{www.spokencorpus.org}{American Spoken Corpus} site,
    reducing complexity by \textbf{50\%}. Implemented a
    \href{https://spokencorpus.org/map_search.php}{Dialect Map}, for
    visualisation of over \textbf{150 transcripts}.
  \item Extracted and visualized migration patterns from over
    \href{https://conflictmemorymigration.manchester.ac.uk/interviews/}{\textbf{70
    interview transcripts}} of the Troubles' victims.
  \item Devised a
    \href{https://github.com/manojmanikandan7/WikipediaXmlParser}{processing
    tool} to pre-process, extract and collate a corpus of around
    \textbf{600 text documents} from Wikipedia XML exports.
\end{itemize}
\textbf{HRBluSky, Pruvity Group} \hfill Apr 2023 | Aug 2023
\\ %\hfill City, State\\ % Company name and location
\textit{Technology Intern}  % Position and duration
\begin{itemize}
  \item Mentored under an ML expert to complete the project, gaining
    experience in code structuring, documentation, testing and
    technical writing.
  \item Evaluated performance of fine-tuned Language Models on
    templated text generation, streamlining the process of artificial
    document generation for HR by \textbf{65\%}.
  \item Assembled an AI-based assistant to generate around \textbf{18
    types} of HR documents, resulting in improvement of running basic
    operations around the workspace by \textbf{30\%}.
\end{itemize}

% Additional Experience or Volunteer Work
%\noindent
%\textbf{Project or Volunteer Work Name} %\hfill City, State\\ %
% Project or organization name and location
%\textit{Position Title, Volunteer} \hfill Month Year – Month Year %
% Position and duration
%\begin{itemize}
%\item Description of responsibilities and achievements at this
% position. % Responsibilities and achievements
%\end{itemize}

% Club or Organization Experience
%\noindent
%\textbf{University of Manchester} \hfill Manchester, United
% Kingdom\\ % Club or organization name and location
%\textit{Student Representative} \hfill Oct 2023 – Ongoing % Position
% and duration
%\begin{itemize}
%\item Description of responsibilities and achievements at this
% position. % Responsibilities and achievements
%\end{itemize}

% Skills Section
\section*{SKILLS}
\begin{itemize}
  \item \textbf{Programming and tools:} Java, Spring Boot, Python,
    Rust, C, C++, PHP, ReactJS, JavaScript, MySQL, TypeScript, HTML,
    CSS, ARMv7 assembly, Verilog, SystemVerilog.
  \item \textbf{Technical:} Deep Learning, Convolutional Neural
    Networks, Recurrent Neural Networks, LSTMs, Language Models,
    Transformers, Transfer Learning, Prompt Engineering, Encryption Algorithms.
    % Software skills % Communication skills
\end{itemize}

% Projects Section
\section*{PROJECTS}
\noindent
\textbf{Interactive Polish Magazine Transcriber}
\href{https://github.com/manojmanikandan7/PolishMagTextRecog}{[Link]}
\hfill Aug 2025 % \hfill City, State\\ % Project name and location
\begin{itemize}
  \item Engineered an interactive transcriber for Polish magazine
    scans, based on Google's \texttt{tesseract} transcription engine.
  \item Processed over \textbf{215 pages} of Polish Queer magazines
    and compiled their transcripts.
  \item Retrieved around \textbf{10,000 blocks} of texts, utilised in
    further analysis and study.
\end{itemize}

\noindent
\textbf{Wikipedia XML Parser}
\href{https://github.com/manojmanikandan7/WikipediaXmlParser}{[Link]}
\hfill Jul 2025 % \hfill City, State\\ % Project name and location
\begin{itemize}
  \item Fabricated a command line tool to pre-process and extract
    text from
    \href{https://en.wikipedia.org/wiki/Special:Export}{\texttt{Wikipedia}
    XML exports}.
  \item Built a corpus of around \textbf{600 text documents} from
    medicine-related articles and talk pages.
  \item Integrated the tool to a workflow for medical data textual
    analysis and published the package to the
    \href{https://test.pypi.org/project/wikipedia-xml-parser/}{TestPyPI} index.
\end{itemize}

% Team Project
\noindent
\textbf{PennyWise - Student-friendly Budget Tracker}
\href{https://github.com/manojmanikandan7/PennyWise}{[Link]} \hfill
Sep 2023 | May 2024 % Project name and location
\begin{itemize}
  \item Scored \textbf{92\%} for the overall project grade, for code
    quality and presentation.
  \item Collaborated with a team of \textbf{6 students} to develop a
    budget tracker for students, as part of the First-Year Team
    Project at University of Manchester.
  \item Presented the project to around \textbf{100 students},
    boosting financial awareness and fitness.
    % Project description and contributions
\end{itemize}

% Internship Project
% \noindent
% \textbf{LetterBot - AI based Chat-bot to produce HR Documents}
% \hfill Apr 2023 | Aug 2023 \\ % Project name and location
% \textit{Technology Intern, HRBluSky}  % Project link and duration
% \begin{itemize}
%     \item An AI-based chat-bot to create HR documents curated to
% inputs by the user.
%     \item Streamlined the process of artificial document generation by 65\%.
%     \item Incorporated the OpenAI API in Python to develop the chat-bot.
%     \item Implemented preprocessing of the commands and formatting
% the generated documents.
%     \item Produced a custom fine-tuned model based on the GPT-3 from OpenAI.
%  % Project description and contributions
% \end{itemize}

% Personal Project
% \noindent
% \textbf{Encryption of data using the AES encryption algorithm in
% Java} \hfill Jan 2022 | Mar 2022 \\ % \hfill City, State\\ %
% Project name and location
% \href{https://github.com/manojmanikandan7/Cryptography}{Link}  %
% Project link and duration
% \begin{itemize}
%     \item Focused on encrypting data using the Advanced Encryption
% Standard (AES), a symmetric block cipher.
%     \item Integrated a complementary decryption program which takes
% in the hashed data and private key to decrypt the data.
%  % Project description and contributions
% \end{itemize}

\section*{LEADERSHIP AND AWARDS}
\noindent
\textbf{University of Manchester} | Manchester, United Kingdom \hfill
Sep 2023 | Jun 2026 % Club or organization name and location
\begin{itemize}
  \item Attained the prestigious Manchester International Excellence
    Scholarship 2023, presented to only \textbf{50 students} out of
    around \textbf{3000 candidates}.
  \item Contracted and supervised
    \href{https://www.greatunihack.com}{GreatUniHack} 2024,
    Manchester, with around 200 participants.
  \item Nominated as a Student Representative for a class of around
    \textbf{300} Computer Science students.
  \item Peer Mentor (PASS) for \textbf{20 underclassmen} to provide
    academic and well-being support.
    % Responsibilities and achievements
\end{itemize}

\noindent
\textbf{JSS INTERNATIONAL SCHOOL} | Dubai, United Arab Emirates
\hfill Jun 2015 | Mar 2023
\begin{itemize}
  \item Received Proficiency awards for scoring above \textbf{90\%}
    overall from Years 9 to 12.
  \item Co-founder and Tech support at CollegePrep101. Raised college
    preparedness among students by about \textbf{40\%}.
\end{itemize}

% Certifications
\section*{CERTIFICATIONS}
\noindent
\textbf{Deep Learning Specialization}
\href{https://www.coursera.org/account/accomplishments/specialization/LR4ZVQP24B9B}{[Credential
Link]} \hfill Aug 2024
\begin{itemize}
  \item \textbf{Courses Completed:} Neural Networks and Deep
    Learning, Improving Deep Neural Networks: Hyperparameter Tuning,
    Regularization and Optimization, Structuring Machine Learning
    Projects, Convolutional Neural Networks, Sequence Models.
\end{itemize}

% End document
\end{document}
